### 2019-03-17 papers.tex
Pull in the revised version of Jim's paper with reduced authorship list

\addtrack
	{}{Security and privacy}
\addpaper
	{CVE-2018-90017117}
	{\texttt{t0m7}}
	{Keywords: kingme, exploit, input validation}
	{SIGBOVIK_2019_paper_3}
	{0cm}
	{}
\addpaper
	{Orchhit: User-oblivious social networking}
	{Jim McCann and Brian Saghy}
	{Keywords: privacy, hashing, cryptography}
	{SIGBOVIK_2019_paper_37}
	{0cm}
	{}

>>>>

\addtrack
	{}{Security and privacy}
\addpaper
	{CVE-2018-90017117}
	{\texttt{t0m7}}
	{Keywords: kingme, exploit, input validation}
	{SIGBOVIK_2019_paper_3}
	{0cm}
	{}
\addpaper
	{Orchhit: User-oblivious social networking}
	{Jim McCann}
	{Keywords: privacy, hashing, cryptography}
	{SIGBOVIK_2019_paper_37}
	{0cm}
	{}
